Watch Out for the Bully! Study of Interference Between Jobs Running Concurrently on Dragonfly Network

### 2016-03-19 draft.tex
update all the figures

The dragonfly network studied in this work consists of 33 groups, each group contains 8 routers and each router has 4 compute nodes attached to it. Overall, there are 264 routers and 1056 compute nodes in the network. The bandwidth of both terminal links and local channel are set to 2GB/s, the global channel bandwidth is set to 4GB/s.

@@

%\subsection{Workload Combinations}
%\label{sec:workload-combination}
%
%We come up with two parallel workloads. The first workload consists of the original application traces described in Section \ref{sec: application traces}, while the second workload is a modified version of the first workload for the purpose of validation.

@@

The first parallel workload analyzed in our experiment consists of three applications presented in section\ref{sec: application traces}. The details of this workload shown in Table \ref{tab: parallel workload-1}.

\begin{table}[ht]
\begin{center}
\caption{Details of Parallel Workload \Rmnum{1 }.} 
\label{tab: parallel workload-1}
%\centering % Centers the table on the page, comment out to left-justify
\begin{tabular}{l c c c }
\toprule % Top horizontal line
\toprule
&\multicolumn{3}{c}{Application Details} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
\cmidrule(l){2-4}
App Name & num. rank & Data per Rank & Total Data\\ % Column names row
\midrule % In-table horizontal line
AMG  &    216 &   0.6MB   &     130MB\\ % Content row 1
\midrule
MultiGrid  &    125 &   5MB   &     625MB\\ 
\midrule
CrystalRouter  &   100  &  35MB    &     3500MB\\

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width = 0.48\textwidth ]{data_amount}
  \caption{Applications Data Transfer Amount. AMG has the least amount of data transfer, compared with MultiGrid and CrystalRouter.\NOTE{y axis in log?} }
  \label{fig:3app-data-amount}
\end{figure}

Figure \ref{fig:3app-data-amount} shows the data transfer amount of each MPI rank of three application. Based on this figure, we can tell that CrystalRouter is the most communication-intensive and AMG is the lest communication-intensive.

\subsection{Workload Analysis}
\begin{figure}[h!]
  \centering
  \includegraphics[width = 0.48\textwidth ]{wkld/wkld-commtime}
  \caption{Time spent on communication by Workload I when 6 different placement and routing configurations are used. Random is better than contiguous in terms of improving communication efficiency. Communication time can be further reduced when (progressive) adaptive routing is used under both placement schemes. }
  \label{fig:wkld-commtime}
\end{figure}

The communication time spent by parallel workload \Rmnum{1} under different placement and routing configuration shown in Figure \ref{fig:wkld-commtime}. The contiguous placement coupled with minimal routing results in highest communication time. Progressive adaptive and adaptive routing have comparable results when coupled with contiguous placement. The random placement results the comparable performance with any routing schemes and they all outperform the contiguous placement configurations.

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/gc-traffic}
        \caption{Global Channel Traffic}
        \label{fig:global-channel-traffic}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/lc-traffic}
        \caption{Local Channel Traffic}
        \label{fig:local-channel-traffic}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/tl-traffic}
        \caption{Terminal Link Traffic}
        \label{fig:terminal-link-traffic}
    \end{subfigure}%
  \caption{Traffic go through different level of links in the dragonfly network. The Workload \Rmnum{1} running under 6 different placement \& routing configuration. }
   \label{fig:wkld-network-traffic}
\end{figure*}

\begin{figure*}[t!]
    \centering   
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/gc-stime}
        \caption{Global Channel Busy Time}
        \label{fig:global-channel-stime}
    \end{subfigure}%
     \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/lc-stime}
        \caption{Local Channel Busy Time}
        \label{fig:local-channel-stime}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/tl-stime}
        \caption{Terminal Link Busy Time}
        \label{fig:terminal-link-stime}
    \end{subfigure}%
   \caption{The busy time of links in different level in the dragonfly network. The Workload \Rmnum{1} running under 6 different placement \& routing configuration.}
   \label{fig:wkld-network-stime}
\end{figure*}

Figure \ref{fig:wkld-network-traffic} shows the amount of traffic go through terminal links, local channels and global channels when the workload running on dragonfly network with 6 different placement and routing configurations, and Figure \ref{fig:wkld-network-stime} shows the corresponding busy time.

@@

Contiguous placement allocates MPI ranks to physical nodes that are adjacent to each other, which confines the workload traffic to some local area when coupled with minimal routing. This may result in local congestion and unbalanced network utilization. As we can see from Figure \ref{fig:wkld-network-traffic} and \ref{fig:wkld-network-stime}, contiguous placement coupled with minimal routing always leads to the extreme high traffic amount for some routers , and thus longest busy time.

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{amg/lc-traffic}
        \caption{AMG Local Channel Traffic}
        \label{fig:amg-lc-traffic}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{mg/lc-traffic}
        \caption{MG Local Channel Traffic}
        \label{fig:mg-lc-traffic}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{cr/lc-traffic}
        \caption{CR Local Channel Traffic}
        \label{fig:cr-lc-traffic}
    \end{subfigure}%
   \caption{The traffic go through the local channels of routers that belongs to specific application.  }
   \label{fig:3app-lc-traffic}
\end{figure*}

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{amg/gc-traffic}
        \caption{AMG Global Channel Traffic}
        \label{fig:amg-gc-traffic}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{mg/gc-traffic}
        \caption{MG Global Channel Traffic}
        \label{fig:mg-gc-traffic}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{cr/gc-traffic}
        \caption{CR Global Channel Traffic}
        \label{fig:cr-gc-traffic}
    \end{subfigure}%
   \caption{The traffic go through the global channels of routers that belongs to specific application.}
   \label{fig:3app-gl-traffic}
\end{figure*}

@@

\begin{table}[ht]
\begin{center}
\caption{Details of Parallel Workload \Rmnum{2 }.} 
\label{tab: parallel workload-2}
%\centering % Centers the table on the page, comment out to left-justify
\begin{tabular}{l c c c }
\toprule % Top horizontal line
\toprule
&\multicolumn{3}{c}{Application Details} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
\cmidrule(l){2-4}
App Name & num. rank & Data per Rank & Total Data\\ % Column names row
\midrule % In-table horizontal line
sAMG  &    216 &   60MB   &     13000MB\\ % Content row 1
\midrule
MultiGrid  &    125 &   5MB   &     625MB\\ 
\midrule
CrystalRouter  &   100  &  35MB    &     3500MB\\

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width = 0.48\textwidth ]{syn-wkld/data_amount}
  \caption{Applications Data Transfer Amount. sAMG has the most amount of data transfer, compared with CR and MG.}
  \label{fig:syn-3app-data-amount}
\end{figure}

In order to prove that AMG being bullied only because it is less communication-intensive than its concurrently running peers, we generate a synthetic application, sAMG, which are same the with AMG's original traces in every aspect expect that the data transfer amount 100x greater than AMG. We run the new workload that consists of sAMG, MultiGrid and CrystalRouter on the same dragonfly network with the same placement \& routing configurations. As shown in Figure \ref{fig:syn-3app-data-amount}, sAMG become the most communication-intensive application in the new workload.

\begin{figure}[h!]
  \centering
  \includegraphics[width = 0.48\textwidth ]{syn-wkld/wkld-commtime}
  \caption{ Time spent on communication by Workload II when using 6 different placement and routing scheme configurations. Random is better than contiguous in terms of improving communication efficiency. Communication time can be further reduced when (progressive) adaptive routing is used under both placement schemes. }
  \label{fig:syn-wkld-commtime}
\end{figure}

The communication time spent by parallel workload \Rmnum{2} under different placement \& routing configurations shown in Figure \ref{fig:syn-wkld-commtime}. As the overall traffic increased in the workload(due to sAMG), the time spent on communication under each configuration also increases. But the performance of each configuration still keep the same trend as parallel workload \Rmnum{1}. The contiguous placement coupled with minimal routing results in highest communication time. The random placement coupled with minimal routing is the most efficient. Progressive adaptive routing is better than adaptive routing when random placement is in use. And they have comparable results when coupled contiguous placement.

Figure \ref{fig:synwkld-network-traffic}, \ref{fig:synwkld-network-stime} show the network status when Workload \Rmnum{2} running under different placement \& routing configurations. Contiguous placement coupled with minimal routing result in most traffic go through certain local and global channel, thus the longest  communication time for terminal link, local and global channel. When coupled with (progressive) adaptive routing, the local congestion can get alleviated in contiguous placement. The random placement reach the comparable performance with any routing schemes in terms of both traffic and busy time. They are better than contiguous \& minimal configuration, but not too much improvement against contiguous\&(progressive) adaptive configuration.

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/gc-traffic}
        \caption{Global Channel Traffic}
        \label{fig:synwkld-global-channel-traffic}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/lc-traffic}
        \caption{Local Channel Traffic}
        \label{fig:synwkld-local-channel-traffic}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/tl-traffic}
        \caption{Terminal Link Traffic}
        \label{fig:synwkld-terminal-link-traffic}
    \end{subfigure}%
  \caption{Traffic go through different level of links in the dragonfly network. The Workload \Rmnum{2} running under 6 different placement \& routing configuration.}
   \label{fig:synwkld-network-traffic}
\end{figure*}

\begin{figure*}[t!]
    \centering   
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/gc-btime}
        \caption{Global Channel Busy Time}
        \label{fig:synwkld-global-channel-stime}
    \end{subfigure}%
     \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/lc-btime}
        \caption{Local Channel Busy Time}
        \label{fig:synwkld-local-channel-stime}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/tl-btime}
        \caption{Terminal Link Busy Time}
        \label{fig:synwkld-terminal-link-stime}
    \end{subfigure}%
   \caption{Traffic go through different level of links in the dragonfly network. The Workload \Rmnum{2} running under 6 different placement \& routing configuration.}
   \label{fig:synwkld-network-stime}
\end{figure*}

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/lc-traffic}
        \caption{sAMG Local Channel Traffic}
        \label{fig:syn-samg-lc-traffic}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/lc-traffic}
        \caption{MG Local Channel Traffic}
        \label{fig:syn-mg-lc-traffic}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/lc-traffic}
        \caption{CR Local Channel Traffic}
        \label{fig:syn-cr-lc-traffic}
    \end{subfigure}%
   \caption{Each Application Router Local Channel Traffic.  }
   \label{fig:syn-3app-lc-traffic}
\end{figure*}

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/gc-traffic}
        \caption{sAMG Global Channel Traffic}
        \label{fig:syn-samg-gc-traffic}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/gc-traffic}
        \caption{MG Global Channel Traffic}
        \label{fig:syn-mg-gc-traffic}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/gc-traffic}
        \caption{CR Global Channel Traffic}
        \label{fig:syn-cr-gc-traffic}
    \end{subfigure}%
   \caption{Each Application Router Global Channel Traffic.}
   \label{fig:syn-3app-gc-traffic}
\end{figure*}

>>>>

The dragonfly network studied in this work consists of 33 groups, each group contains 8 routers and each router has 4 compute nodes attached to it. Overall, there are 264 routers and 1056 compute nodes in the network. The ratio between aggregrated local and global channel bandwidth are set propotional to the Cray Cascade system\cite{faanes} based on the dragonfly topology\cite{dally-dragonfly}.

@@

%\subsection{Workload Combinations}
%\label{sec:workload-combination}
%
%We come up with two parallel workloads. The first workload consists of the original application traces described in Section \ref{sec: application traces}, while the second workload is a modified version of the first workload for the purpose of validation. 
\subsection{Workload Summary}
\label{sec:workload summary}

Workload \Rmnum{1} comprises the original AMG, MultiGrid and CrystalRouter. As we see in Table \ref{tab:apps-detail}, AMG has the least amount of data transfer, thus contributes the least amount of traffic in Wrokload \Rmnum{1}.

Workload \Rmnum{2} comprises sAMG, MultiGrid and CrystalRouter. sAMG consists of synthetic traces that are same the with AMG's original traces in every aspect expect that the data transfer amount 100x greater than AMG. The traffic from sAMG is the dominant in Workload \Rmnum{2}.

\begin{table}[ht]
\begin{center}
\caption{Details of Application Traces.} 
\label{tab:apps-detail}
%\centering % Centers the table on the page, comment out to left-justify
\begin{tabular}{l c c c }
\toprule % Top horizontal line
\toprule
&\multicolumn{3}{c}{Application Details} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
\cmidrule(l){2-4}
App Name & num. rank & Data per Rank & Total Data\\ % Column names row
\midrule % In-table horizontal line
AMG  &    216 &   0.6MB   &     130MB\\ % Content row 1
\midrule
MultiGrid  &    125 &   5MB   &     625MB\\ 
\midrule
CrystalRouter  &   100  &  35MB    &     3500MB\\ 
\midrule
sAMG  &    216 &   60MB   &     13000MB\\ % Content row 1
\midrule % In-table horizontal line
\bottomrule % Bottom horizontal line
\end{tabular}
\end{center}
\end{table}

@@

% The first parallel workload analyzed in our experiment consists of three applications presented in section\ref{sec: application traces}. The details of this workload shown in Table \ref{tab: parallel workload-1}.

% 
% \begin{figure}[h!]
%   \centering
%   \includegraphics[width = 0.48\textwidth ]{data_amount}
%   \caption{Applications Data Transfer Amount. AMG has the least amount of data transfer, compared with MultiGrid and CrystalRouter.\NOTE{y axis in log?} }
%   \label{fig:3app-data-amount}
% \end{figure}
% 
% Figure \ref{fig:3app-data-amount} shows the data transfer amount of each MPI rank of three application. Based on this figure, we can tell that CrystalRouter is the most communication-intensive and AMG is the lest communication-intensive. 
% 
% 
% \subsection{Workload Analysis}
%  
% \begin{figure}[h!]
%   \centering
%   \includegraphics[width = 0.48\textwidth ]{wkld/wkld-commtime}
%   \caption{Time spent on communication by Workload I when 6 different placement and routing configurations are used. Random is better than contiguous in terms of improving communication efficiency. Communication time can be further reduced when (progressive) adaptive routing is used under both placement schemes. }
%   \label{fig:wkld-commtime}
% \end{figure}

\begin{table}[ht]
\begin{center}
\caption{Time spent on communication (MilliSecond) by Workload II when 6 different placement\&routing configuration in use.} 
\label{tab:wkld-commtime}
%\centering % Centers the table on the page, comment out to left-justify
\begin{tabular}{l c c c c c c }
\toprule % Top horizontal line
\toprule
&\multicolumn{6}{c}{Placement\&Routing Configuration} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
\cmidrule(l){2-7}
	 & CM & CA & CPA & RM & RA & RPA \\ % Column names row
\midrule % In-table horizontal line
Runtime  &  1870 & 1250 & 1248 & 860 & 835 &830\\ % Content row 1

@@

The communication time spent by parallel workload \Rmnum{1} under different placement and routing configuration shown in Table \ref{tab:wkld-commtime}. The contiguous placement coupled with minimal routing results in highest communication time. Progressive adaptive and adaptive routing have comparable results when coupled with contiguous placement. The random placement results the comparable performance with any routing schemes and they all outperform the contiguous placement configurations.

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/gc-traffic}
        \caption{Global Channel Traffic}
        \label{fig:global-channel-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/lc-traffic}
        \caption{Local Channel Traffic}
        \label{fig:local-channel-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/tl-traffic}
        \caption{Terminal Link Traffic}
        \label{fig:terminal-link-traffic}
    \end{subfigure}\\

    \centering   
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/gc-stime}
        \caption{Global Channel Busy Time}
        \label{fig:global-channel-stime}
    \end{subfigure}\hfill
     \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/lc-stime}
        \caption{Local Channel Busy Time}
        \label{fig:local-channel-stime}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{wkld/tl-stime}
        \caption{Terminal Link Busy Time}
        \label{fig:terminal-link-stime}
    \end{subfigure}%
   \caption{Traffic and saturated time of links in different level in the dragonfly network. The Workload \Rmnum{1} running under 6 different placement \& routing configuration.}
   \label{fig:wkld-network-traffic-stime}
\end{figure*}

Figure \ref{fig:wkld-network-traffic-stime} shows the amount of traffic go through terminal links, local channels and global channels, and the corresponding saturated time when the workload running on dragonfly network with 6 different placement and routing configurations

@@

Contiguous placement allocates MPI ranks to physical nodes that are adjacent to each other, which confines the workload traffic to some local area when coupled with minimal routing. This may result in local congestion and unbalanced network utilization. Contiguous placement coupled with minimal routing always leads to the extreme high traffic amount for some routers , and thus longest busy time.

@@

\begin{figure*}[t]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{amg/lc-traffic}
        \caption{AMG Local Channel Traffic}
        \label{fig:amg-lc-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{mg/lc-traffic}
        \caption{MG Local Channel Traffic}
        \label{fig:mg-lc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{cr/lc-traffic}
        \caption{CR Local Channel Traffic}
        \label{fig:cr-lc-traffic}
    \end{subfigure}\\

    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{amg/gc-traffic}
        \caption{AMG Global Channel Traffic}
        \label{fig:amg-gc-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{mg/gc-traffic}
        \caption{MG Global Channel Traffic}
        \label{fig:mg-gc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{cr/gc-traffic}
        \caption{CR Global Channel Traffic}
        \label{fig:cr-gc-traffic}
    \end{subfigure}%
   \caption{The traffic go through the local and global channels of routers that belongs to specific application.}
   \label{fig:3app-lc-gc-traffic}
\end{figure*}

@@

@@

In order to prove that AMG being bullied only because it is less communication-intensive than its concurrently running peers, we generate a synthetic application, sAMG, which are same the with AMG's original traces in every aspect expect that the data transfer amount 100x greater than AMG. We run the new workload that consists of sAMG, MultiGrid and CrystalRouter on the same dragonfly network with the same placement \& routing configurations. As shown in Table \ref{tab:apps-detail}, sAMG become the most communication-intensive application in the new workload.

\begin{table}[ht]
\begin{center}
\caption{Time spent on communication (MilliSecond) by Workload II when 6 different placement\&routing configuration in use.} 
\label{tab:syn-wkld-commtime}
%\centering % Centers the table on the page, comment out to left-justify
\begin{tabular}{l c c c c c c }
\toprule % Top horizontal line
\toprule
&\multicolumn{6}{c}{Placement\&Routing Configuration} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
\cmidrule(l){2-7}
	 & CM & CA & CPA & RM & RA & RPA \\ % Column names row
\midrule % In-table horizontal line
Runtime  &  6123 & 3231 & 3725 & 2544 & 3701 & 3228 \\ % Content row 1

@@

The communication time spent by parallel workload \Rmnum{2} under different placement \& routing configurations shown in Table \ref{tab:syn-wkld-commtime}. As the overall traffic increased in the workload(due to sAMG), the time spent on communication under each configuration also increases. But the performance of each configuration still keep the same trend as parallel workload \Rmnum{1}. The contiguous placement coupled with minimal routing results in highest communication time. The random placement coupled with minimal routing is the most efficient. Progressive adaptive routing is better than adaptive routing when random placement is in use. And they have comparable results when coupled contiguous placement.

Figure \ref{fig:synwkld-network-traffic-stime} show the network status when Workload \Rmnum{2} running under different placement \& routing configurations. Contiguous placement coupled with minimal routing result in most traffic go through certain local and global channel, thus the longest  communication time for terminal link, local and global channel. When coupled with (progressive) adaptive routing, the local congestion can get alleviated in contiguous placement. The random placement reach the comparable performance with any routing schemes in terms of both traffic and busy time. They are better than contiguous \& minimal configuration, but not too much improvement against contiguous\&(progressive) adaptive configuration.

\begin{figure*}[t]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/gc-traffic}
        \caption{Global Channel Traffic}
        \label{fig:synwkld-global-channel-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/lc-traffic}
        \caption{Local Channel Traffic}
        \label{fig:synwkld-local-channel-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/tl-traffic}
        \caption{Terminal Link Traffic}
        \label{fig:synwkld-terminal-link-traffic}
    \end{subfigure}\\

    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/gc-btime}
        \caption{Global Channel Busy Time}
        \label{fig:synwkld-global-channel-stime}
    \end{subfigure}\hfill
     \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/lc-btime}
        \caption{Local Channel Busy Time}
        \label{fig:synwkld-local-channel-stime}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{syn-wkld/tl-btime}
        \caption{Terminal Link Busy Time}
        \label{fig:synwkld-terminal-link-stime}
    \end{subfigure}%
   \caption{Traffic and Saturated Time of different level of links in the dragonfly network. The Workload \Rmnum{2} running under 6 different placement \& routing configuration.}
   \label{fig:synwkld-network-traffic-stime}
\end{figure*}

@@

\begin{figure*}[t]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/lc-traffic}
        \caption{sAMG Local Channel Traffic}
        \label{fig:syn-samg-lc-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/lc-traffic}
        \caption{MG Local Channel Traffic}
        \label{fig:syn-mg-lc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/lc-traffic}
        \caption{CR Local Channel Traffic}
        \label{fig:syn-cr-lc-traffic}
    \end{subfigure}\\
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/gc-traffic}
        \caption{sAMG Global Channel Traffic}
        \label{fig:syn-samg-gc-traffic}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/gc-traffic}
        \caption{MG Global Channel Traffic}
        \label{fig:syn-mg-gc-traffic}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/gc-traffic}
        \caption{CR Global Channel Traffic}
        \label{fig:syn-cr-gc-traffic}
    \end{subfigure}%
   \caption{Each Application Router Local and Global Channel Traffic.}
   \label{fig:syn-3app-gc-traffic}
\end{figure*}
